### 2021-07-24 paper.tex
result done, almost complete

	Next three machine learning models are created. A \textbf{CNN} or a
	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}.

>>>>

	Next three machine learning models are created. A \textbf{CNN} or a
	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}. The
	models are implemented in both fast.ai and tensorflow, to be compared later.

	While training the images are resized to $(150 \times 150)$ and augmented at
	runtime, thus removing bias as much as possible. Since there are only two
	possible classes (yes and no), a binary class is sufficient; dividing the
	images into training and testing (validation set) in $80:20$ ratio. Giving
	us $2603 \ \textnormal{and} \ 650$ images for the \textit{yes} and
	\textit{no} classes, respectively.

	After training is complete the models are then evaluated (further discussed
	in Section~\ref{sec:result} )

	\section{Result}%
	\label{sec:result}

	The evaluated models are plotted on graph for better understanding of data.

	\begin{figure}[H]
		\centering
		\subfloat[vgg16 using tensorflow]
		{\includegraphics[width=0.4\linewidth]
		{imgs/tf_vgg16.png}\label{tf_vgg16}}
		\hspace{0.5cm}
		\subfloat[vgg16 using fast.ai]
		{\includegraphics[width=0.5\linewidth]
		{imgs/fastai_vgg16.png}\label{fastai_vgg16}}
		\caption{VGG16 implemented in fast.ai and tensorflow}
		\label{VGG16 in fast.ai and tensorflow}
	\end{figure}

	\begin{figure}[H]
		\centering
		\subfloat[resnet50 using tensorflow]
		{\includegraphics[width=0.4\linewidth]
		{imgs/tf_resnet.png}\label{tf_resnet}}
		\hspace{0.5cm}
		\subfloat[resnet50 using fast.ai]
		{\includegraphics[width=0.5\linewidth]
		{imgs/fastai_resnet.png}\label{fastai_resnet}}
		\caption{Resnet 50 implemented in fast.ai and tensorflow}
		\label{ResNet 50 in fast.ai and tensorflow}
	\end{figure}

	We have achieved around 96\% and 98\% accuracy for for the VGG16 and ResNet,
	respectively; using \textit{tensorflow}, and 97\% (98\% after unfreezing)
	and 97\% (99\% after unfreezing) using \textit{fast.ai}. While using CNN
	accuracy was almost same when implemented by the both the libraries.

	There are lot of room for improvement but due to time and hardware
	constrains we were able to only implement till such.

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\linewidth]{imgs/result.png}
		\caption{Predictions made by the VGG16 model in tensorflow on random data}%
		\label{fig:result}
	\end{figure}

	As it can be seen from Figure~\ref{fig:result} there are some false
	positives in our predictions.
